Lattice Boltzmann study of mass transfer for complicated geometries

### 2012-01-17 Text/introduction.tex
Started doing last simulations.

Only nondimensional parameter Peclet number governs the advection-diffusion equation:
\beq
Pe=\frac{U_{bubble} N_y}{D},
\feq
where $D$ is the diffusion coefficient to prescribe. As far as we want to increase velocity, that
means one needs to increase the diffusion coefficient as well. The runs were made with
velocities $2,4,6,8,10,15,20,40$ times larger than original velocities. The velocities we chose and
its corresponding capillary numbers are presented in Table \ref{table:scaling:peclet}. Periodic
boundary conditions were used and mass transfer coefficient was calculated according to Eq.
(\ref{main:simulation:equation}).
\begin{table}[htb!]
\begin{tabularx}{0.5\textwidth}{|X|X|}
\hline
$U_{bubble}$& $Ca$\\
\hline
0.0055&0.097\\
0.0143&0.254\\
0.0297&0.526\\
0.0424&0.750\\
0.0588&1.040\\
\hline
\end{tabularx}
\end{table}
For $Ca=0.0055$ a few results are given in Fig. \ref{fig:ca0055:keeping:peclet}. The rule of the
thumb that for such simulations the velocity shouldn't be more than $0.05$.

\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/scalingpeclet009.eps}
\caption{The same Peclet number for $Ca=0.0055$. One can see that
the mass transfer coefficient comes to the same point.{\color{red} Need to compare contours for the
concentration!!!} \label{fig:ca0055:keeping:peclet}}
\end{figure}

>>>>

Only nondimensional parameter Peclet number governs the advection-diffusion equation:
\beq
Pe=\frac{U_{bubble} N_y}{D},
\feq
where $D$ is the diffusion coefficient to prescribe. As far as we want to increase velocity, that
means one needs to increase the diffusion coefficient as well. The runs were made with
velocities $2,4,6,8,10,15,20,40$ times larger than original velocities. The velocities we chose and
its corresponding capillary numbers are presented in Table \ref{table:scaling:peclet}. Periodic
boundary conditions were used and mass transfer coefficient was calculated according to Eq.
(\ref{main:simulation:equation}).
\begin{table}[htb!]
\begin{tabularx}{\textwidth}{|X|X|X|X|}
\hline
Scale&$U_{bubble}$&Time Iterations&$C_{aver}$\\
\hline
\multicolumn{4}{c}{}\\
\multicolumn{4}{c}{$Ca=0.097$}\\
\hline
$2$ &$0.011$&$400000$&$0.318$\\
$4$ &$0.023$&$200000$&$0.319$\\
$8$ &$0.044$&$100000$&$0.320$\\
$10$&$0.055$&$80000$ &$0.321$\\
$20$&$0.11 $&$40000$ &$0.324$\\
$40$&$0.22 $&$20000$ &$0.328$\\
\hline
\multicolumn{4}{c}{}\\
\multicolumn{4}{c}{$Ca=0.254$}\\
\hline
$2$& $0.0286$&$800000$&$0.6533$\\
$4$& $0.0572$&$400000$&$0.6591$\\
$8$& $0.1144$&$200000$&$0.6692$\\
$10$&$0.1430$&$160000$&$0.6734$\\
$20$&$0.2860$&$80000$ &$0.6894$\\
\hline
\multicolumn{4}{c}{}\\
\multicolumn{4}{c}{$Ca=0.526$}\\
\hline
$2$&$0.0594$&$200000$&$0.3271$\\
$4$&$0.1188$&$100000$&$0.3315$\\
\hline
\multicolumn{4}{c}{}\\
\multicolumn{4}{c}{$Ca=0.750$}\\
\hline
$2$&$0.0848$&$200000$&$0.3489$\\
\hline
\multicolumn{4}{c}{}\\
\multicolumn{4}{c}{$Ca=1.040$}\\
\hline
$2$&$0.1176$&$200000$&$0.3675$\\
\hline
\end{tabularx}
\caption{Scaling Peclet table. One can see that scaling is pretty successful. One can see as well
that the stability limit is approximately around $U_{bubble}=0.1$. That can give us an idea of
scale of simulations. \label{table:scaling:peclet}}
\end{table}

The corresponding to Table \ref{table:scaling:peclet} contour profiles for different scalings are
presented in Fig. \ref{fig:contours:scaling:peclet}.
\begin{figure}
\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca026.eps}\\
\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca054.eps}\\
\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca05.eps}\\
\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca097.eps}\\
\includegraphics[height=0.3\textwidth]{Figures/contourlines_scale_ca14.eps}\\
\caption{Contours for scaling Peclet number.\label{fig:contours:scaling:peclet}}
\end{figure}

\section{Performing real simulations}
As it was found earlier one needs to make a few units simulations to obtain a proper volumetric
mass transfer coefficient. This section studies the quantity of the unit cells on the volumetric
mass transfer coefficient to be independent of the number of unit cells. The cases we want to
examine in terms of the capillary number are indicated above. The number of cells we want to
simulate are $1$,$4$,$6$,$8$,$10$. As it was discussed in the previous section we want to keep
velocity around $0.05-0.1$. The number of steps for mass to cross whole domain is approximately
$1.5 \frac{N_x}{U_{bubble}}$, given the bulk velocity. If $U_{bubble}$ is taken as $0.05$ then for
the domain size $3000$ one can obtain the following number of iteration for mass transfer to be
stabilize $1.5 \frac{3000}{0.05}=90000$. Therefore, $10^{6}$ time iterations are enough for system
to be stabilized.

%For $Ca=0.0055$ a few results are given in Fig. \ref{fig:ca0055:keeping:peclet}. The rule of the
%thumb that for such simulations the velocity shouldn't be more than $0.05$.

%\begin{figure}[htb!]
%\includegraphics[width=\textwidth]{Figures/scalingpeclet009.eps}
%\caption{The same Peclet number for $Ca=0.0055$. One can see that
%the mass transfer coefficient comes to the same point.{\color{red} Need to compare contours for the
%concentration!!!} \label{fig:ca0055:keeping:peclet}}
%\end{figure}
